\textsf{Are large language models superhuman chemists?}

### 2024-10-21 src/tex/ms.tex
Update src/tex/ms.tex
Co-authored-by: Martiño Rios-Garcia <147555961+MrtinoRG@users.noreply.github.com>

We curated more than 2,800 question-answer pairs, evaluated leading open—and closed-source LLMs, and found that the best models outperformed the best human chemists in our study on average.
However, the models struggle with some tasks that are easy for human experts and provide overconfident predictions.
These findings reveal LLMs' impressive chemical capabilities while emphasizing the need for further research to improve their safety and usefulness. They also suggest adapting chemistry education and developing better evaluation methods for LLMs in chemistry.
\end{abstract}

>>>>

We curated more than 2,800 question-answer pairs, evaluated leading open- and closed-source LLMs, and found that the best models outperformed the best human chemists in our study on average.
However, the models struggle with some tasks that are easy for human experts and provide overconfident predictions.
These findings reveal LLMs' impressive chemical capabilities while emphasizing the need for further research to improve their safety and usefulness. They also suggest adapting chemistry education and developing better evaluation methods for LLMs in chemistry.
\end{abstract}
